---
title: "lotsim"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lotsim}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lotsim)

set.seed(123L)
```

## Creating lots

```{r}
# Creates a single <lot>.
x = lotsim::new_lot(as.integer(c(1, 0, 0, 0, 1, 0)))
x
```


```{r}
# Creates a <lot_series> containing a single lot.
y = lotsim::new_lot_series__shuffle(size = 30L, count = 5L)
y
```


```{r}
# Creates a <lot_series> containing multiple lots.
z = lotsim::new_lot_series__rbinom(size = 30L, prop = c(.33, .5))
z
```


```{r}
# Concatenates all lot objects, yielding a <lot_object_wrapper>. The wrapper is a
# structure containing <lot> and or <lot_series> objects.
xyz = x + y + z # c(x, y, z) achieves the same result
xyz

plot(xyz)
plot(xyz, what = "true_prop", col = "red", add = TRUE)
```


## Creating patterns

```{r}
y = rep(0., 100L) |> lotsim::slope(slope = .001)
plot(1:100, y, type = "l")
```


```{r}
y = rep(0., 100L) |> lotsim::stairs(height = .01, case_len = 10L)
plot(1:100, y, type = "l")
```


```{r}
y = rep(0., 100L) |> lotsim::wave(wave_len = .1, amplitude = .005)
plot(1:100, y, type = "l")
```


```{r}
y = rep(0., 100L) |>
  lotsim::rnorm_runs(sigma = .005, min_run = 1L, max_run = 20L, prob_run = .5)

plot(1:100, y, type = "l")
```


### Combining patterns using pipes

```{r}
y = rep(0., 100L) |> 
  lotsim::slope(slope = .0001) |>
  lotsim::wave(wave_len = .1, amplitude = .005)

plot(1:100, y, type = "l")
```

## Everything together

```{r fig.height = 7}
a = rep(.05, 30L) |>
  lotsim::rnorm_runs(.01, 1L, 20L, .5) |>
  lotsim::slope(.0005) |>
  lotsim::clamp(lower = 0L, upper = 1L) # Convenience function

b = rep(0.05, 30L) |>
  lotsim::slope(.0001) |>
  lotsim::wave(.5, .005) |>
  lotsim::clamp(0L, 1L)

xy = lotsim::new_lot_series__rbinom(100L, a) +
  lotsim::new_lot_series__rbinom(100L, b)

plot(xy)
plot(xy, what = "true_prop", col = "red", add = TRUE)
```


```{r fig.width= 5}
plot(xy, flip = FALSE, ylim = c(0, .15))
```


```{r fig.height = 7}
obj = lotsim::new_lot_series__rbinom(100L, lotsim::rnorm_runs(rep(.05, 100), .02, 1L, 20L, .5)) +
  lotsim::new_lot_series__rbinom(100L, lotsim::slope(rep(.05, 100), -.0001)) +
  lotsim::new_lot_series__rbinom(100L, lotsim::stairs(rep(.04, 100), .1, 10L)) +
  lotsim::new_lot_series__rbinom(100L, lotsim::wave(rep(.03, 100), .2, .005))

plot(obj[[1L]], type = "n", xlim = c(0, .2))
for (o in obj) {
  plot(o, add = TRUE, col = "gray")
  plot(o, add = TRUE, what = "true_prop", col = "dodgerblue")
}
```


```{r}
as.data.frame(obj) |> utils::head(10L)
```


## Taking sub-samples

```{r}
lotsim::lot_sample(xyz, 4L)
```


About indexing `lot_object_wrapper`s, currently single bracket indexing `x[1]` has the default `list` indexing behavior, but this will be changed later to return individual batches. However, the same effect can be achieved first calling `as.lot_series()`, then indexing the resulting `lot_series`.

